---
title: "Seminar4-2 group acitivity"
author: "wzho6305"
date: "09/12/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##### Group activity 4-2 ######

##### Step and discussion question 1: #####
```{r import packages, read in data, plot the independent and dependent variables}
# install relevant packages

library(foreign)
library(plyr)
library(dplyr)
library(ggplot2)
library(scales)
library(lme4)
library(arm)
library(reshape2)

# read in data

data <- read.csv("NSW_Crime_data_clean-1.csv")
head(data)
names(data)

# plot the variables

par(mfrow = c(3,2))
hist(data$Murder)
hist(data$Robbery.without.a.weapon)
hist(data$Break...Enter..Dwelling.)
hist(data$Motor.Vehicle.Theft)
hist(data$Fraud)

```

```{r choose 5 independent variables and dependent variable}

# 4 independent variables: Median_rent_weekly, Median_tot_hhd_inc_weekly, completed.Year.12, Population.25.34

# dependent variable: number of Robbery without a weapon

```

##### Step and discussion question 2: #####

```{r transformation and standardization of the data }

data$z.Median_rent_weekly  <- scale(data$Median_rent_weekly,
      scale = (sd(data$Median_rent_weekly, na.rm = T) *2))
data$z.Median_tot_hhd_inc_weekly  <- scale(data$Median_tot_hhd_inc_weekly,
      scale = (sd(data$Median_tot_hhd_inc_weekly, na.rm = T) *2))

robberymodel.3 <- lm(Robbery.without.a.weapon ~ z.Median_rent_weekly + z.Median_tot_hhd_inc_weekly + X..of.People.who.completed.Year.12
                     + X..Population.25.34, data = data)

display(robberymodel.3)

# plot individual rent}
ggplot(
  data,
  aes(x= z.Median_rent_weekly, y =Robbery.without.a.weapon )) +
  geom_point(alpha = 0.5)+

geom_smooth(se = FALSE) +
 ## scale_y_continuous(labels = dollar)+
  theme_bw()

model.rent <- lm(Robbery.without.a.weapon ~ z.Median_rent_weekly, data = data)
display(model.rent)

plot(model.rent)

# plot individual household}
ggplot(
  data,
  aes(x= z.Median_tot_hhd_inc_weekly, y =Robbery.without.a.weapon )) +
  geom_point(alpha = 0.5)+

geom_smooth(se = FALSE) +
 ## scale_y_continuous(labels = dollar)+
  theme_bw()

model.hhd <- lm(Robbery.without.a.weapon ~ z.Median_tot_hhd_inc_weekly, data = data)
display(model.hhd)

plot(model.hhd)

# plot individual X..of.People.who.completed.Year.12}
ggplot(
  data,
  aes(x= X..of.People.who.completed.Year.12, y =Robbery.without.a.weapon )) +
  geom_point(alpha = 0.5)+

geom_smooth(se = FALSE) +
 ## scale_y_continuous(labels = dollar)+
  theme_bw()

model.edu <- lm(Robbery.without.a.weapon ~ X..of.People.who.completed.Year.12, data = data)
display(model.edu)

plot(model.edu)

# plot individual age}
ggplot(
  data,
  aes(x= X..Population.25.34, y =Robbery.without.a.weapon )) +
  geom_point(alpha = 0.5)+

geom_smooth(se = FALSE) +
 ## scale_y_continuous(labels = dollar)+
  theme_bw()

model.edu <- lm(Robbery.without.a.weapon ~ X..Population.25.34, data = data)
display(model.edu)

plot(model.edu)

```

```{r log transformation}
# we noticed that the data of Median_rent_weekly and Median_tot_hhd_inc_weekly in need to be standardized.
# we choose to use logarithm which affects the magnitude of the coefficient that corresponds to the logged variable, but it doesn’t affect the value of the outcome. 

log.Median_rent_weekly <- log(data$Median_rent_weekly)
log.Median_tot_hhd_inc_weekly <- log(data$Median_tot_hhd_inc_weekly)
log.X..Population.25.34 <- log(data$X..Population.25.34)
log.X..of.People.who.completed.Year.12 <- log(data$X..of.People.who.completed.Year.12)
log.Robbery.without.a.weapon <- log(data$Robbery.without.a.weapon)


par(mfrow = c(1,2))
plot(data$Median_rent_weekly, data$Robbery.without.a.weapon)
plot(log.Median_rent_weekly, log.Robbery.without.a.weapon)

plot(data$Median_tot_hhd_inc_weekly, data$Robbery.without.a.weapon)
plot(log.Median_tot_hhd_inc_weekly, log.Robbery.without.a.weapon)

plot(data$X..Population.25.34, data$Robbery.without.a.weapon)
plot(log.X..Population.25.34, log.Robbery.without.a.weapon)

plot(data$X..of.People.who.completed.Year.12, data$Robbery.without.a.weapon)
plot(log.X..of.People.who.completed.Year.12, log.Robbery.without.a.weapon)

```
theory: we speculate that the independent variables Median_rent_weekly, Median_tot_hhd_inc_weekly, completed.Year.12, Population.25.34 potentially have strong relationships on the number of the robbery without a weapon in each LGA. 

# build the model

Step and discussion question 3:

```{r theory formation}

# Model with scaled height and race using linear regression
model.all <- lm (Robbery.without.a.weapon ~ Median_rent_weekly + Median_tot_hhd_inc_weekly + X..Population.25.34
                 + X..of.People.who.completed.Year.12 , data = data)

plot(model.all)
summary(model.all)

# The residuals vs Fitted graph represents Residual = Observed – Predicted. It represents the distance between opbserved point versus our predicted point. We have a pretty good result that almost all the point are near the zero line, which represents that our residual is quite small. We find equally spread residuals around a horizontal line with distinct patterns, that is a good indication you have linear relationships.

#Normal Q-Q
#This plot shows if residuals are normally distributed. Do residuals follow a straight line well or do they deviate severely? It’s good if residuals are lined well on the straight dashed line.

#Residuals vs Leverage
#We watch out for outlying values at the upper right corner or at the lower right corner. Those spots are the places where cases can be influential against a regression line. Look for cases outside of a dashed line. In this case, we have a outlier on the top left(8) and top right corner (84)

```

##### Step and discussion question 4: #####
```{r analyse the results and discussions}

# interpretations:

# the intercept of the model is -1.2, indicating that holding other all the independent variables equal to 0. It refers to when the city have zero weekly rent payment, zero household income, zero population from 25-34 and no one complete year 12. 

# the coefficient of the independent variable indicates, taking Median_rent_weekly for example, for the one unit increase in Median_rent_weekly, the number of robbery increases by 0.0057. Same thing for the rest of the independent variables. 

# the coefficient of Median_rent_weekly is 0.0057 and its standard error is 0.0035, which indicates that Median_rent_weekly is not a strong indicator of the relationship. On the contrary, the coefficient of X..Population.25.34 is twice than its standard deviation, which indicates that X..Population.25.34 has a strong relationship with dependent variable. 

```

##### Step and discussion question 5: #####
```{r ethical concerns}

# for the median_rent_weekly, we use the threshhold of 450 to classify rich neighborhood and poor neighborhood. 
# we can group by the richness and conduct confusion matrix to see what the false positive and false negative to further discuss if there is any ethical issues. 


# further discussions:
# give more weight to outliers. we should consider more effects when we evaluate each individuals.

```

##### Step and discussion question 6: #####
```{r factors excluded from this data}

# other factors: gender, race, etc. 

```

